### 2021-10-29 README.Rmd
fixed/updted broken links, and updated tidyverse codign using rlang

<!-- badges: start -->
[![](https://badges.ropensci.org/428_status.svg)](https://github.com/ropensci/software-review/issues/428)
[![DOI](https://joss.theoj.org/papers/10.21105/joss.03282/status.svg)](https://doi.org/10.21105/joss.03282)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![R build status](https://github.com/ropensci/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/ropensci/dataaimsr/actions)
[![Codecov test coverage](https://codecov.io/gh/ropensci/dataaimsr/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/dataaimsr?branch=master)
![pkgdown](https://github.com/ropensci/dataaimsr/workflows/pkgdown/badge.svg)
[![license](https://img.shields.io/badge/license-MIT + file LICENSE-lightgrey.svg)](https://choosealicense.com/)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg)](commits/master)
[![Ask Us Anything
\!](https://img.shields.io/badge/Ask%20us-anything-1abc9c.svg)](https://github.com/ropensci/dataaimsr/issues/new)
![Open Source
Love](https://badges.frapsoft.com/os/v2/open-source.svg?v=103)
<!-- badges: end -->

@@

[4]: https://ropensci.github.io/dataaimsr/articles

@@

`dataaimsr` is provided by the [Australian Institute of Marine Science](https://www.aims.gov.au) under the MIT License ([MIT](http://opensource.org/licenses/MIT)).

@@

Our R package logos use a watercolour map of Australia, obtained with the [ggmap](https://CRAN.R-project.org/package=ggmap) R package, which downloads original map tiles provided by [Stamen Design](http://stamen.com), under [CC BY 3.0](http://creativecommons.org/licenses/by/3.0), with data from [OpenStreetMap](http://openstreetmap.org), under [CC BY SA](http://creativecommons.org/licenses/by-sa/3.0).

>>>>

<!-- badges: start -->
[![](https://badges.ropensci.org/428_status.svg)](https://github.com/ropensci/software-review/issues/428)
[![DOI](https://joss.theoj.org/papers/10.21105/joss.03282/status.svg)](https://doi.org/10.21105/joss.03282)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![R build status](https://github.com/ropensci/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/ropensci/dataaimsr/actions)
[![Codecov test coverage](https://codecov.io/gh/ropensci/dataaimsr/branch/master/graph/badge.svg)](https://app.codecov.io/gh/ropensci/dataaimsr?branch=master)
![pkgdown](https://github.com/ropensci/dataaimsr/workflows/pkgdown/badge.svg)
[![license](https://img.shields.io/badge/license-MIT + file LICENSE-lightgrey.svg)](https://choosealicense.com/)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg)](commits/master)
[![Ask Us Anything
\!](https://img.shields.io/badge/Ask%20us-anything-1abc9c.svg)](https://github.com/ropensci/dataaimsr/issues/new)
![Open Source
Love](https://badges.frapsoft.com/os/v2/open-source.svg?v=103)
<!-- badges: end -->

@@

[4]: https://ropensci.github.io/dataaimsr/articles/

@@

`dataaimsr` is provided by the [Australian Institute of Marine Science](https://www.aims.gov.au) under the MIT License ([MIT](https://opensource.org/licenses/MIT)).

@@

Our R package logos use a watercolour map of Australia, obtained with the [ggmap](https://CRAN.R-project.org/package=ggmap) R package, which downloads original map tiles provided by [Stamen Design](https://stamen.com/), under [CC BY 3.0](https://creativecommons.org/licenses/by/3.0), with data from [OpenStreetMap](https://www.openstreetmap.org/), under [CC BY SA](https://creativecommons.org/licenses/by-sa/3.0).
